Notes on Control Plane Inference

### 2021-04-02 inference.tex
add wp
polish example

\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
\usepackage{scalerel}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}

@@

% record fields
\newcommand{\matches}{\mathsf{matches}}
\newcommand{\action}{\mathsf{action}}
\newcommand{\actions}{\mathsf{actions}}
\newcommand{\keys}{\mathsf{keys}}
\newcommand{\data}{\mathsf{data}}
\newcommand{\params}{\mathsf{params}}
\newcommand{\id}{\mathsf{id}}

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choiceop}{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}
\newcommand{\choice}{\mathbin{\choiceop}}
\DeclareMathOperator*{\bigchoice}{\scalerel*{\choiceop}{\sum}}
\newcommand{\havoc}{\texttt{<?>}}
\newcommand{\SKIP}{\mathsf{skip}}

% math
\newcommand{\argmin}{\mathop{\textrm{argmin}}}
\newcommand{\WP}{\textit{wp}}
\newcommand{\satisfy}[3]{({#1,#3}) \models_{#2}}
\newcommand{\notsatisfy}[3]{({#1,#3})\not\models_{#2}}
\newcommand{\nondet}{\mathsf{nondet}}
\newcommand{\ghostly}{\mathsf{ghostly}}
\newcommand{\state}[1]{\llparenthesis#1\rrparenthesis}

@@

\begin{figure}[htp]
  \[\begin{array}{lclll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row} & (\iota)\\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value} & (a,g,p,\iota)\\
      & \mid & h.f & \textit{Header Access} & (a,g,p,\iota)\\
      & \mid & \havoc & \textit{Havoc} & (a,g,p,\iota) \\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match} & (\iota)\\
      & \mid & \rho.\action & \textit{Symbolic Action} & (\iota) \\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data} & (\iota) \\
      & \mid & x & \textit{Action Data Variable} & (a^*) \\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation} & (a,g,p,\iota) \\
    & \mid & \unop e & \textit{Arbitrary Unary Operation} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x.\,a]\\
    \end{array}\right\} & \textit{Table} & (p)\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Absurdity}& (a,g,p,\iota)\\
      & \mid & b \Rightarrow b & \textit{Implication} & (a,g,p,\iota)\\
      & \mid & e = e & \textit{Bitvector Equality} & (a,g,p,\iota)\\
    & \mid & \forall \rho \in t.~b & \textit{Row Universality} & (\iota)\\
    \multicolumn{4}{l}{c \in \Cmd, a \in \Action, g \in \GCL, p \in \Prog, \iota \in \Instr } \\
    c & ::=  & h.f := e & \textit{Assignment} & (g,p,\iota) \\
      & \mid & \assert b & \textit{Assertion} & (g,p,\iota)\\
      & \mid & \assume b & \textit{Assumption} & (g,p,\iota) \\
      & \mid & t.\apply() & \textit{Table Application} & (p)\\
      & \mid & c;c & \textit{Sequential Composition} & (a,g,p,\iota) \\
      & \mid & c \choice c & \textit{Nondeterministic Choice} & (g,p,\iota)\\
      & \mid & \{c\} & \textit{Scope} & (g,p,\iota)\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Commands $c \in \Cmd$. Legal action indicated by $a \in
  \Action$, legal instrumented command variants indicated by $\iota \in \Instr$,
  dataplane programs indicated by $p \in \Prog$, and table-free commands
  indicated by $g \in \GCL$.}
\label{fig:grammar}
\end{figure}

@@

\begin{figure}[H]
  \[\begin{array}{l>{\triangleq}cl}
  \multicolumn{3}{l}{\edenote{e} : \Model \to \Pkt \rightharpoonup \Value }\\
    \edenote{v}~\mu~\pkt &&
    v \\
    \edenote{\havoc_w}~\mu~\pkt && \{[n]_w \mid n \in \mathbb N\}\\
    \edenote{h.f}~\mu~\pkt &&
    pkt(h.f)\\
    \edenote{\rho.\matches[i]}~\mu~\pkt &&
    \mu(\rho).\matches[i] \\
    \edenote{\rho.\action}~\mu~\pkt &&
    \mu(\rho).\action \\
    \edenote{\rho.\data[i]} &&
    \mu(\rho).\data[i]\\
    \edenote{e_1 \binop e_2}~\mu~\pkt&&
    \edenote{e_1}~\mu~\pkt \binop
    \edenote{e_2}~\mu~\pkt \\
    \edenote{\unop e}~\mu~\pkt &&
    \unop \left(\edenote{e}~\mu~\pkt\right)
  \end{array}
  \]
  \caption{Semantics of Expressions}
  \label{fig:sem-expr}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \satisfy \sigma \pkt \mu \FALSE && \textit{pigs fly} \\
  \satisfy \sigma \pkt \mu b_1 \Rightarrow b_2 &&
  \notsatisfy \sigma \pkt \mu  b_1~\textit{or}~
  \satisfy \sigma \pkt \mu b_2\\
  \satisfy \sigma \pkt \mu e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \satisfy \sigma \pkt \mu \forall \rho \in t. ~b &&
  \forall r \in \sigma(t.\id).
  \satisfy \sigma \pkt {\mu\{\rho \mapsto r\}} b
  \end{array}
  \]
  \todo[inline]{Clarify $\error$ states} \todo[inline]{A goal here is to have a
    standard (i.e. single-model) satisfaction relation, but this was easier to
    think about in the context of the domain (esp. with scoped havoc). The
    difference boils down to a naming convention}
  \caption{Satisfaction for $\BExpr$.}
  \label{fig:bool-satis}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Model \to \Pkt \to \mathcal{P}(\Model \times \Pkt)_\error }\\
    \denote{h.f := e}^\sigma\,\mu\,\pkt && \{(\mu, \pkt\{h \mapsto v\} \mid v \in \edenote{e}\,\mu\,\pkt\})\} \\
    \denote{\assume b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \error & \textit{otherwise}
    \end{cases} \\
    \denote{c_1;c_2}^\sigma\,\mu\,\pkt&&
    \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma\,\mu'\,\pkt' \\
    \denote{c_1 \choice c_2}^\sigma\,\mu\,\pkt &&
    \denote{c_1}^\sigma\,\mu\,\pkt \cup \denote{c_2}^\sigma\,\mu\,\pkt \\
    \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\,\mu\,\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\satisfy \sigma \pkt \mu b_i\} \\
      & \text{where}~b_i = \sigma(t.\id)[i].\matches = t.\keys \\
      \{(\mu,\pkt)\}, & \mathit{otherwise}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{r>{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)[\sigma] : \Cmd \to \Cmd} \\
  \multicolumn{3}{l}{(\cdot)[\sigma] : \Prog \to \GCL} \\
  (h.f := e)[\sigma] && h.f := e   \\
  (\assume b)[\sigma] && \assume b \\
  (\assert b)[\sigma] && \assert b \\
  (c_1;c_2)[\sigma] && c_1[\sigma];c_2[\sigma] \\
  (c_1 \choice c_2)[\sigma] && c_1[\sigma] \choice c_2[\sigma] \\
  (\{c\})[\sigma] && \{c[\sigma]\} \\
  (t.\apply())[\sigma] &&
  \begin{array}[t]{l}
    (\\
    \quad \assume {r_1.\matches = t.\keys};\\
    \quad t.\action[r_1.\action](r_1.\data)\\
    )~\choice\\
    \multicolumn{1}{c}{\vdots}\\
    \choice~(\\
    \quad \assume {r_n.\matches = t.\keys};\\
    \quad t.\action[r_n.\action](r_n.\data)\\
    )\\
    \textrm{where}~[r_1;\ldots;r_n] = \sigma(t.\id)
  \end{array}
  \end{array}
  \]
  \caption{Table Elimination}
  \label{fig:table-elim}
\end{figure}

\begin{theorem}[Table Elimination]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, then for any state $\tau :
  \Value \to \Row^*$,
  \[\denote{c}^\sigma~\mu~\pkt = \denote{c[\sigma]}^\tau~\mu~\pkt\]
\end{theorem}
\begin{proof}
\todo[inline]{By induction on the structure of $c$.}
\end{proof}

@@

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)[?] : \Cmd \to \Cmd} \\
  (h.f := e)[?] && h.f := e \\
  (\assume b)[?] && \assume b \\
  (\assert b)[?] && \assert b\\
  (c_1;c_2)[?] && c_1[?];c_2[?]\\
  (c_1 \choice c_2)[?] && c_1[?] \choice c_2[?]\\
  (\{c\})[?] && \{c[?]\}\\
  (t.\apply())[?] &&
  \begin{array}[t]{l} \displaystyle
    \{ \\
    \quad \rho.\matches := \overrightarrow\havoc; \\
    \quad \rho.\action := \havoc;\\
    \quad \rho.\data := \overrightarrow\havoc; \\
    \quad \assume \rho.\action < |t.\actions|; \\
    \quad \assume \rho.\matches = t.\keys; \\
    \quad \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
    \left(\begin{array}{l}
    \assume \rho.\action = i;\\
    t.\action[i](\rho.\data)
    \end{array}\right)\\
    \} \choice ( \\
    \quad \assume \forall \rho \in t. \rho.\matches \neq t.\keys; \\
    \quad \SKIP \\
    )
  \end{array}
  \end{array}
  \]
  \caption{Symbolic Table instrumentation. Typing information is omitted for
    brevity; each $\havoc$ must have a appropriate bit-width annotation. For
    simplicity, we assume each action in a table has the same number (and types) of
    parameters.}
  \label{fig:table-instrument}
\end{figure}

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{\state\sigma_c : (\Value \to \Row^*) \to \BExpr} \\
  \state\sigma_c = \bigwedge_{ t \in \tables(c) } \bigvee_{r_i \in \sigma(t.\id)}
  \rho = r_i
  \end{array}
  \]
  \caption{Symbolic State Encoding}
  \label{fig:table-instrument}
\end{figure}

%% \begin{lemma}[Models Invariant over Actions]
%%   \label{lem:models-invariant-over-actions}
%%   For a closed action command $c$, $\mu,\mu'
%%   \in \Model$, $\sigma \in \Value \to
%%   \Row^*$, $\pkt \in \Pkt$, there exists some $\pkt'$
%%   \[\denote{c}^\sigma\,\mu\,\pkt = \{\mu,\pkt'\}\]
%%   \end{lemma}

%% \begin{proof}
%%   Proceed by induction over $c$.
%%   \begin{enumerate}[align=left]
%%   \item[$(c = h.f = e)$] Immediate.
%%   \item[$(c = c_1;c_2)$]
%%     By IH($c_1$) there exists some $\pkt''$ such that
%%     $\denote{c_1}^\sigma\,\mu\,\pkt = \{(\mu,\pkt'')\}$.
%%     By IH($c_2$) there exists some $\pkt'$ such that
%%     $\denote{c_2}^\sigma,\mu\,pkt'' = \{(\mu, \pkt')\}$.
%%     The result follows by definition of $\denote{-}$.
%%     \end{enumerate}
%% \end{proof}

\begin{samepage}
\begin{theorem}[Instrumentation Equivalence]
  \label{thm:instr-equiv}
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, \[\denote{c}^\sigma~\mu~\pkt = \denote{c[?];\assume \state\sigma_c}^\sigma~\mu~\pkt.\]
\end{theorem}
\end{samepage}

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{halloweenmath}
\usepackage{amsmath, amssymb, amsthm, array, stmaryrd}
\usepackage{wasysym}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{float}
\usepackage{scalerel}
%% \usepackage[notext,not1,nomath]{stix}
\usepackage{enumitem}

@@

% record fields
\newcommand{\matches}{\mathsf{matches}}
\newcommand{\action}{\mathsf{action}}
\newcommand{\actions}{\mathsf{actions}}
\newcommand{\keys}{\mathsf{keys}}
\newcommand{\data}{\mathsf{data}}
\newcommand{\params}{\mathsf{params}}
\newcommand{\id}{\mathsf{id}}
\newcommand{\reach}{\mathit{\mathit{reach}}}
\newcommand{\hit}{\mathit{hit}}
\newcommand{\reads}{\mathit{reads}}

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choiceop}{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}
\newcommand{\choice}{\mathbin{\choiceop}}
\DeclareMathOperator*{\bigchoice}{\scalerel*{\choiceop}{\sum}}
\newcommand{\havoc}[1]{\mathop{\textsf{havoc}}#1}
\newcommand{\SKIP}{\mathsf{skip}}

% math
\newcommand{\argmin}{\mathop{\textrm{argmin}}}
\newcommand{\WP}{\textit{wp}}
\newcommand{\satisfy}[3]{({#1,#3}) \models_{#2}}
\newcommand{\notsatisfy}[3]{({#1,#3})\not\models_{#2}}
\newcommand{\nondet}{\mathsf{nondet}}
\newcommand{\ghostly}{\mathsf{ghostly}}
\newcommand{\state}[1]{\llparenthesis#1\rrparenthesis}
\newcommand{\instr}{[\forall]}
\newcommand{\ginstr}{[\mathghost]}

@@

\begin{figure}[htp]
  \[\begin{array}{lclll}
    \multicolumn{3}{l}{\Value} \\
    v & ::= & [n]_w  & \textit{Bitvector Literal} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\SymbRow} \\
    \rho & ::= & \left\{
    \begin{array}{l}
      \matches = \List[x];\\
      \action = x;\\
      \data = \List[x]
    \end{array}\right\} & \textit{Symbolic Row} & (\iota)\\
    \multicolumn{3}{l}{\BVExpr} \\
    e & ::= & v & \textit{Value} & (a,g,p,\iota)\\
      & \mid & h.f & \textit{Header Access} & (a,g,p,\iota)\\
      & \mid & \rho.\matches[i] & \textit{Symbolic Match} & (\iota)\\
      & \mid & \rho.\action & \textit{Symbolic Action} & (\iota) \\
      & \mid & \rho.\data[i] & \textit{Symbolic Action Data} & (\iota) \\
      & \mid & x & \textit{Action Data Variable} & (a^*) \\
      & \mid & e \binop e & \textit{Arbitrary Binary Operation} & (a,g,p,\iota) \\
    & \mid & \unop e & \textit{Arbitrary Unary Operation} & (a,g,p,\iota) \\
    \multicolumn{3}{l}{\Table} \\
    t & ::= & \left\{\begin{array}{l}
    t.\id = v; \\
    t.\keys = \List[h.f]; \\
    t.\actions = \List[\lambda \vec x.\,a]\\
    \end{array}\right\} & \textit{Table} & (p)\\
    \multicolumn{3}{l}{\BExpr} \\
    b & ::= & \FALSE  & \textit{Absurdity}& (a,g,p,\iota)\\
      & \mid & b \Rightarrow b & \textit{Implication} & (a,g,p,\iota)\\
    & \mid & e = e & \textit{Bitvector Equality} & (a,g,p,\iota)\\
    & \mid & \rho \in t & \textit{Table membership} & (\iota)\\
    & \mid & \forall \rho.~b & \textit{Row Universality} & (\iota)\\
    \multicolumn{4}{l}{c \in \Cmd, a \in \Action, g \in \GCL, p \in \Prog, \iota \in \Instr } \\
    c & ::=  & h.f := e & \textit{Assignment} & (g,p,\iota) \\
      & \mid & \havoc \rho & \textit{Row Havoc} & (\iota) \\
      & \mid & \assert b & \textit{Assertion} & (g,p,\iota)\\
      & \mid & \assume b & \textit{Assumption} & (g,p,\iota) \\
      & \mid & t.\apply() & \textit{Table Application} & (p)\\
      & \mid & c;c & \textit{Sequential Composition} & (a,g,p,\iota) \\
      & \mid & c \choice c & \textit{Nondeterministic Choice} & (g,p,\iota)\\
      & \mid & \{c\} & \textit{Scope} & (g,p,\iota)\\
    \multicolumn{3}{l}{
      \begin{array}{ll}
        x \in \Var & h \in \Hdr\\
        n,w,i \in \mathbb{N} & f \in \Field
    \end{array}} & \textit{Sets }\\
  \end{array}
\]
\caption{Grammar of Commands $c \in \Cmd$. Legal action indicated by $a \in
  \Action$, legal instrumented command variants indicated by $\iota \in \Instr$,
  dataplane programs indicated by $p \in \Prog$, and table-free commands
  indicated by $g \in \GCL$.}
\label{fig:grammar}
\end{figure}

@@

\begin{figure}[H]
  \[\begin{array}{l>{\triangleq}cl}
  \multicolumn{3}{l}{\edenote{e} : \Model \to \Pkt \rightharpoonup \Value }\\
    \edenote{v}~\mu~\pkt &&
    v \\
    \edenote{h.f}~\mu~\pkt &&
    pkt(h.f)\\
    \edenote{\rho.\matches[i]}~\mu~\pkt &&
    \mu(\rho).\matches[i] \\
    \edenote{\rho.\action}~\mu~\pkt &&
    \mu(\rho).\action \\
    \edenote{\rho.\data[i]} &&
    \mu(\rho).\data[i]\\
    \edenote{e_1 \binop e_2}~\mu~\pkt&&
    \edenote{e_1}~\mu~\pkt \binop
    \edenote{e_2}~\mu~\pkt \\
    \edenote{\unop e}~\mu~\pkt &&
    \unop \left(\edenote{e}~\mu~\pkt\right)
  \end{array}
  \]
  \caption{Semantics of Expressions}
  \label{fig:sem-expr}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \satisfy \sigma \pkt \mu \FALSE && \textit{pigs fly} \\
  \satisfy \sigma \pkt \mu b_1 \Rightarrow b_2 &&
  \notsatisfy \sigma \pkt \mu  b_1~\textit{or}~
  \satisfy \sigma \pkt \mu b_2\\
  \satisfy \sigma \pkt \mu e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \satisfy\sigma\pkt\mu \rho \in t. && \mu(\rho) \in \sigma(t.\id) \\
  \satisfy \sigma \pkt \mu \forall \rho. ~b &&
  \forall r.
  \satisfy \sigma \pkt {\mu\{\rho \mapsto r\}} b
  \end{array}
  \]
  \todo[inline]{Clarify $\error$ states}
  \caption{Satisfaction for $\BExpr$.}
  \label{fig:bool-satis}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{l >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Model \to \Pkt \to \mathcal{P}(\Model \times \Pkt)_\error }\\
    \denote{h.f := e}^\sigma\,\mu\,\pkt && \{(\mu, \pkt\{h \mapsto v\} \mid v \in \edenote{e}\,\mu\,\pkt\})\} \\
    \denote{\assume b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \{(\mu,\pkt)\} & \satisfy \sigma \pkt \mu b \\
      \error & \textit{otherwise}
    \end{cases} \\
    \denote{\havoc \rho}^\sigma\,\mu\,\pkt &&
    \{(\mu\{\rho \mapsto r\}, \pkt) \mid r \in \Row\} \\
    \denote{c_1;c_2}^\sigma\,\mu\,\pkt&&
    \bigcup_{(\mu',\pkt') \in \denote{c_1}^\sigma\,\mu\,\pkt}\denote{c_2}^\sigma\,\mu'\,\pkt' \\
    \denote{c_1 \choice c_2}^\sigma\,\mu\,\pkt &&
    \denote{c_1}^\sigma\,\mu\,\pkt \cup \denote{c_2}^\sigma\,\mu\,\pkt \\
    \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\mu\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\,\mu\,\pkt,
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~r = \argmin_i\{\satisfy \sigma \pkt \mu b_i\} \\
      & \text{where}~b_i = \sigma(t.\id)[i].\matches = t.\keys \\
      \{(\mu,\pkt)\}, & \mathit{otherwise}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands}
  \label{fig:com-sem}
\end{figure}

@@

\begin{figure}
  \[\begin{array}{r>{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)[\sigma] : \Cmd \to \Cmd} \\
  \multicolumn{3}{l}{(\cdot)[\sigma] : \Prog \to \GCL} \\
  (h.f := e)[\sigma] && h.f := e   \\
  (\assume b)[\sigma] && \assume b \\
  (\assert b)[\sigma] && \assert b \\
  (c_1;c_2)[\sigma] && c_1[\sigma];c_2[\sigma] \\
  (c_1 \choice c_2)[\sigma] && c_1[\sigma] \choice c_2[\sigma] \\
  (\{c\})[\sigma] && \{c[\sigma]\} \\
  (t.\apply())[\sigma] &&
  \begin{array}[t]{l}
    (\\
    \quad \assume {r_1.\matches = t.\keys};\\
    \quad t.\action[r_1.\action](r_1.\data)\\
    )~\choice\\
    \phantom)~\,\vdots\\
    \phantom)\,\choice~(\\
    \quad \assume {r_n.\matches = t.\keys};\\
    \quad t.\action[r_n.\action](r_n.\data)\\
    )\choice (\\
    \quad \displaystyle \assume {\bigwedge_{i=1}^n r_n.\matches \neq t.\keys};\\
    \quad \SKIP \\
    )\\
    \textrm{where}~[r_1;\ldots;r_n] = \sigma(t.\id)
  \end{array}
  \end{array}
  \]
  \caption{Table Substitution}
  \label{fig:table-elim}
\end{figure}

\begin{theorem}[Table Substitution]
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, then for any state $\tau :
  \Value \to \Row^*$,
  \[\denote{c}^\sigma~\mu~\pkt = \denote{c[\sigma]}^\tau~\mu~\pkt\]
\end{theorem}
\begin{proof}
\todo[inline]{By induction on the structure of $c$.}
\end{proof}

@@

We augment the headers for a program $c$ with ghost headers $\gamma_t$ for each
table $t \in \tables(c)$. The header $\gamma_t$ has defined fields
$\reach$, which is set to true if the packet reaches table $t$,
$\hit$ which is set to true the packet hits in the table, and
$\reads$ which is really a list of $|t.\keys|$ variables that stores the
values of the packet when evaluating $t.\keys$.

\begin{figure}[htp]
  \begin{minipage}[t]{0.5\textwidth}
  \[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)\instr : \Cmd \to \Cmd} \\
  (h.f := e)\instr && h.f := e \\
  (\assume b)\instr && b \\
  (\assert b)\instr && \assert b\\
  (c_1;c_2)\instr && c_1\instr;c_2\instr\\
  (c_1 \choice c_2)\instr && c_1\instr \choice c_2\instr\\
  (\{c\})\instr && \{c\instr\}\\
  (t.\apply())\instr && \\
  \multicolumn{3}{r}{
    \qquad
    \begin{array}[t]{l} \displaystyle
      \{ \\
      \quad \havoc \rho;\\
      \quad \assume \rho \in t; \\
      \quad \assume \rho.\matches = t.\keys; \\
      \quad \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
      \left(\begin{array}{l}
        \assume \rho.\action = i;\\
        t.\action[i](\rho.\data)
      \end{array}\right)\\
      \} \choice ( \\
      \quad \assume \forall \rho. \rho \in t \Rightarrow \rho.\matches \neq t.\keys;\\
      \quad \SKIP \\
      )
    \end{array}}
  \end{array}
  \]
  \end{minipage}\begin{minipage}[t]{0.45\textwidth}
\[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{(\cdot)\ginstr : \Cmd \to \Cmd} \\
  (h.f := e)\ginstr && h.f := e \\
  (\assume b)\ginstr && \assume b \\
  (\assert b)\ginstr && \assert b\\
  (c_1;c_2)\ginstr && c_1\ginstr;c_2\ginstr\\
  (c_1 \choice c_2)\ginstr && c_1\ginstr \choice c_2\ginstr\\
  (\{c\})\ginstr && \{c\ginstr\}\\
  (t.\apply())\ginstr &&\\
  \multicolumn{3}{l}{
    \qquad
    \begin{array}[t]{l} \displaystyle
    \gamma_t.\reach := [1]_1; \\
    \gamma_t.\reads := t.\keys; \\
    (\\
    \quad \assume \rho.\matches = t.\keys; \\
    \quad \gamma_t.\hit := [1]_1; \\
    \quad \displaystyle \bigchoice_{i=0}^{|t.\action| -1}
    \left(\begin{array}{l}
    \assume \rho.\action = i;\\
    t.\action[i](\rho.\data)
    \end{array}\right)\\
    ) \choice ( \\
    \quad \assume \rho.\matches \neq t.\keys; \\
    \quad \gamma_t.\hit := [0]_1;\\
    \quad \SKIP \\
    )
  \end{array}}
  \end{array}
  \]
  \end{minipage}
  \caption{Symbolic Table instrumentation alternatives. For simplicity, we
    assume each action in a table has the same number (and types) of parameters.
    We want to eliminate the universal quantifier in the miss case shown in
    pn the left. The current attempt, on the right, uses a ghost header
    $\gamma_t$ for every table $t$. }
  \label{fig:table-instrument}
\end{figure}

\begin{figure}[htp]
  \[\begin{array}{r cl}
  \multicolumn{3}{l}{\state\sigma_c : (\Value \to \Row^*) \to \BExpr} \\
  \state\sigma_c &\triangleq
  & \displaystyle\bigwedge_{ t \in \tables(c) }
  \begin{array}{l}
  \left(\bigvee_{r_i \in \sigma(t.\id)}
  \rho = r_i\right) \wedge \\
  \left(\bigwedge_{r_i \in \sigma(t.\id)}
  \gamma_t.\mathit{reads} \neq r_i.\keys\right)
  \Rightarrow \gamma_t.\mathit{hit} = [0]_1
  \end{array}
  \end{array}
  \]
  \caption{Symbolic State Encoding}
  \label{fig:table-instrument}
\end{figure}

\begin{samepage}
\begin{theorem}[Ghostly Instrumentation Equivalence]
  \label{thm:ghost-instr-equiv}
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, \[\denote{c}^\sigma~\mu~\pkt = \denote{c\ginstr;\assume \state\sigma_c}^\sigma~\mu~\pkt.\]
\end{theorem}
\end{samepage}

\begin{samepage}
\begin{theorem}[Quantified Instrumentation Equivalence]
  \label{thm:forall-instr-equiv}
  For every $c \in \Cmd$, well-formed state $\sigma : \Value \to \Row^*$, model
  $\mu \in \Model$, and packet $\pkt \in \Pkt$, \[\denote{c}^\sigma~\mu~\pkt = \denote{c\instr}^\sigma~\mu~\pkt.\]
\end{theorem}
\end{samepage}

@@

    We can compute as follows:
    \[\begin{array}{>{\displaystyle}ll}
    \denote{\ghostly(c)}^\sigma\,\mu\,\pkt\\
    =\denote{
        \begin{array}{>{\displaystyle}l}
          \gamma.t_{\mathit{reach}} := [1]_1; \\
          \gamma.t_{\mathit{read}(0)} := t.\keys[0]; \\
          \vdots \\
          \gamma.t_{\mathit{read}(|t.\keys|-1)} := t.\keys[|t.\keys|-1]; \\[1em]
          \left(\gamma.t_{\mathit{hit}} := [0]_1 \right)
          \choice \left(\bigchoice_{j = 1}^{|t.\action|-1}
            \left(\begin{array}{l}
              \gamma.t_{\mathit{hit}} := [1]_1 ;\\
              \gamma.t_{\mathit{action}} := j;\\
              t.\action[j](\overrightarrow{\gamma.t_{\mathit{data}}})
            \end{array}\right)
          \right)
    \end{array}}^\sigma\,\mu\,\pkt \\[2em]
    =\denote{
        \begin{array}{>{\displaystyle}l}
          \left(\gamma.t_{\mathit{hit}} := [0]_1 \right)
          \choice \left(\bigchoice_{j = 1}^{|t.\action|-1}
            \left(\begin{array}{l}
              \gamma.t_{\mathit{hit}} := [1]_1 ;\\
              \gamma.t_{\mathit{action}} := j;\\
              t.\action[j](\overrightarrow{\gamma.t_{\mathit{data}}})
            \end{array}\right)
          \right)
    \end{array}}^\sigma\!\mu\,\pkt' \\
    \qquad\qquad \text{where}~\pkt' = \pkt\left\{\begin{array}{l}
    \gamma.t_{\mathit{reach}} \mapsto [1]_1,\\
    \overrightarrow{\gamma.t_{\textit{key}} \mapsto \edenote{t.\keys}\,\pkt\,\mu}
    \end{array}\right\} \\
    =\denote{
      \left(\gamma.t_{\mathit{hit}} := [0]_1 \right)}^\sigma\!\mu\,\pkt'
    \cup
    \denote{\left(\bigchoice_{j = 1}^{|t.\action|-1}
            \left(\begin{array}{l}
              \gamma.t_{\mathit{hit}} := [1]_1 ;\\
              \gamma.t_{\mathit{action}} := j;\\
              t.\action[j](\overrightarrow{\gamma.t_{\mathit{data}}})
            \end{array}\right)
            \right)
    }^\sigma\!\mu\,\pkt' \\
    = \left\{(\mu,\pkt'\left\{\gamma.t_{\mathit{hit}} \mapsto [0]_1\right\})\right\}
    \cup
        \denote{\left(\bigchoice_{j = 1}^{|t.\action|-1}
          \left(\begin{array}{l}
            \gamma.t_{\mathit{hit}} := [1]_1 ;\\
            \gamma.t_{\mathit{action}} := j;\\
            t.\action[j](\overrightarrow{\gamma.t_{\mathit{data}}})
          \end{array}\right)
          \right)
        }^\sigma\!\mu\,\pkt' \\
  = \left\{(\mu,\pkt'\left\{\gamma.t_{\mathit{hit}} \mapsto [0]_1\right\})\right\}
  \cup
  \left(\bigcup_{j = 1}^{|t.\action|-1}
  \denote{t.\action[j](\overrightarrow{\gamma.t_{\mathit{data}}})}^\sigma\,\mu\,\pkt'\left\{
  \begin{array}{l}
    \gamma.t_{\textit{hit}} \mapsto [1]_1,\\
    \gamma.t_{\textit{action}} \mapsto j
  \end{array}
  \right\}
  \right) \\
    \end{array}
\]
